Commit Rater

### 2015-08-26 presentations/paper/results.tex
Include graphics in paper

\subsection{Repo-level analysis}
\label{sec:results1}
This subsection focuses solely on repository-level analysis of our metrics, since comparison between individual commits and or individual authors would be tedious. Also, author-level analysis is open to everyone through the web interface.

@@

On the other hand, \ref{fig:bp_imperative_subject} shows that authors of the linux kernel use the imperative mood for the subject the most, while the authors of the 101worker rarely do. Additionally, \ref{fig:bp_no_short_message} shows that linux kernel authors do not write short commit messages, while the authors of the 101worker do. This observation coincides with our estimations for the worker, since that criterion was inspired by a prevalence for 1-word commits in that repo.

One significant difference between the two small repos (badgekit and 101worker) and the big repos (perl and linux kernel) stands out in \ref{fig:bp_body_used}. The big repos both make heavy use of the body, while it is almost never used by the worker and only sometimes by the badgekit.

Finally, \ref{fig:bp_no_period_subject} shows that generally none of the repositories put a period at the end of the subject line. This means, that this criterion could be disregarded, if similar behaviour can be observed in other repositories.

>>>>

\subsection{Repo-level analysis}
\label{sec:results1}

\TODO{Graphics placement}

This subsection focuses solely on repository-level analysis of our metrics, since comparison between individual commits and or individual authors would be tedious. Also, author-level analysis is open to everyone through the web interface.

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/subject_limit.pdf}
    \caption{Subject Limit Boxplot}
    \label{fig:bp_subject_limit}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/imperative_subject.pdf}
    \caption{Imperative Subject Boxplot}
    \label{fig:bp_imperative_subject}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/no_short_message.pdf}
    \caption{No Short Message Boxplot}
    \label{fig:bp_no_short_message}
\end{figure}

On the other hand, figure \ref{fig:bp_imperative_subject} shows that authors of the linux kernel use the imperative mood for the subject the most, while the authors of the 101worker rarely do. Additionally, figure \ref{fig:bp_no_short_message} shows that linux kernel authors do not write short commit messages, while the authors of the 101worker do. This observation coincides with our estimations for the worker, since that criterion was inspired by a prevalence for 1-word commits in that repo.

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/body_used.pdf}
    \caption{Body Used Boxplot}
    \label{fig:bp_body_used}
\end{figure}

One significant difference between the two small repos (badgekit and 101worker) and the big repos (perl and linux kernel) stands out in figure \ref{fig:bp_body_used}. The big repos both make heavy use of the body, while it is almost never used by the worker and only sometimes by the badgekit.

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/no_period_subject.pdf}
    \caption{No Period Subject Boxplot}
    \label{fig:bp_no_period_subject}
\end{figure}

Finally, figure \ref{fig:bp_no_period_subject} shows that generally none of the repositories put a period at the end of the subject line. This means, that this criterion could be disregarded, if similar behaviour can be observed in other repositories.
